---
title: "Employee Accident Analysis"
author: "David Lopez"
output: html_document
---

For our Employee Accident Analysis we'll break the project into a couple of parts
 
 Part 1: Import & Inspect our data
  - loading our data into our working environment
  - load necessary packages for project
  - check quality of data (nulls/errors/duplicates etc.)
  
  
 Part 2: Clean & Transform our data
  - Rename/remove columns & filter any data not needed
  - Create/Recode columns needed for analysis
  - Joins, if needed
  
 Part 3: Data Analysis
  - Basic EDA Q's we'll want to answer
    - when do we see the most accidents happening? 
    - what roles, and in which locations, tend to have more accident than others? 
    - do we see any factors that might lead to these accidents? 
 
====================================================================================================


```{r}

```



```{r}

```

## Including Plots



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
